Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-03-28 additional_files/additional_file_1.tex
Fix some typos upon proofreading the manuscript

\begin{itemize}
	\item smaller than 50 bp or larger than 500 kb in size
	\item located on unanchored scaffolds or organellar genomes
	\item classified as unresolved breakends (\texttt{SVTYPE=BND})
	\item containing at least one N in either the reference or alternate allele sequence
\end{itemize}

@@

We used a set of tools that we assembled in an R package called svmutools
\url{https://github.com/malemay/svmutools} to convert the svmu output to VCF
format. We limited ourselves to processing deletions and insertions because of
the complexity of resolving other types of variants from whole-genome
assemblies.  Copy number variants and inversions called by svmu were therefore
excluded from downstream analyses. The
resulting set of variants was filtered to remove those smaller than 50 bp or larger than 500
kb and those with any N in either the reference or alternate allele sequence.
Finally, we normalized the VCF files using \texttt{bcftools norm} and merged
them using SVmerge to obtain a single file with variants discovered through
comparison of high-quality genome assemblies.

@@

\subsection*{Comparison of WGS and SoySNP50K genotypes}
\label{annexe-sv-gwas-soysnp50k}
When we first analyzed the results from the GWAS analysis on all 389 samples,
we found discrepancies between the haplotypes at some loci and the expected
phenotype that should correspond to that haplotype for simple traits such as
flower color and seed coat color. Upon further analysis, we found that a
mismatch between the sequencing data and the identity of the accession was the
most probable cause of these discrepancies. In order to identify the samples
for which this could be the case, we compared the genotypes of SNPs obtained
from the SoySNP50K array \cite{song2013} to those predicted from the Illumina WGS
data. We did this for the 385 samples that had a match in the GRIN database. Briefly, we
retrieved SoySNP50K genotype calls from SoyBase \citep{grant2010} and extracted
all SNPs with a MAF $\geq$ 0.1 in our population. We then translated the positions
of these SNPs from assembly version 2 to assembly version 4 of Williams by
finding exact matches of 41-bp sequences surrounding the SNP positions. The
32,852 SNPs for which unambiguous positions could be found on genome assembly
version 4 were genotyped from the mapped WGS reads using \texttt{bcftools
mpileup} and \texttt{bcftools call}. We then used \texttt{bcftools gtcheck} to
compute the concordance between the WGS genotype calls and the
SoySNP50K genotype dataset. We identified 24 samples
with < 90\% concordance between the two genotype datasets and removed them from
the dataset. We also excluded an additional sample for which concordance was over 90\%
but poor raw sequencing data quality (\%GC content) suggested contamination.
The concordance between WGS data and SoySNP50K genotypes is included in
Additional file 3 and shown in Figure \ref{concordance-histogram}.

@@

None of the three GWAS analyses that we conducted on hilum color found signals
at the \emph{W1} and \emph{O} loci studied by \cite{bandillo2017} (Figures
\ref{hilum_color_all_manhattan}, \ref{hilum_color_blackbrown_manhattan},
\ref{hilum_color_rbr_manhattan}).

>>>>

\begin{itemize}
	\item smaller than 50 bp or larger than 500 kb in size
	\item located on unanchored scaffolds or organellar genomes
	\item classified as unresolved breakends (\texttt{SVTYPE=BND})
	\item containing at least one N in the alternate allele sequence
\end{itemize}

@@

We used a set of tools that we assembled in an R package called svmutools
(\url{https://github.com/malemay/svmutools}) to convert the svmu output to VCF
format. We limited ourselves to processing deletions and insertions because of
the complexity of resolving other types of variants from whole-genome
assemblies.  Copy number variants and inversions called by svmu were therefore
excluded from downstream analyses. The
resulting set of variants was filtered to remove those smaller than 50 bp or larger than 500
kb and those with any N in either the reference or alternate allele sequence.
Finally, we normalized the VCF files using \texttt{bcftools norm} and merged
them using SVmerge to obtain a single file with variants discovered through
comparison of high-quality genome assemblies.

@@

\subsection*{Comparison of WGS and SoySNP50K genotypes}
\label{annexe-sv-gwas-soysnp50k}
When we first analyzed the results from the GWAS analysis on all 389 samples,
we found discrepancies between the haplotypes at some loci and the expected
phenotype that should correspond to that haplotype for simple traits such as
flower color and seed coat color. Upon further analysis, we found that a
mismatch between the sequencing data and the identity of the accession was the
most probable cause of these discrepancies. In order to identify the samples
for which this could be the case, we compared the genotypes of SNPs obtained
from the SoySNP50K array \citep{song2013} to those predicted from the Illumina WGS
data. We did this for the 385 samples that had a match in the GRIN database. Briefly, we
retrieved SoySNP50K genotype calls from SoyBase \citep{grant2010} and extracted
all SNPs with a MAF $\geq$ 0.1 in our population. We then translated the positions
of these SNPs from assembly version 2 to assembly version 4 of Williams by
finding exact matches of 41-bp sequences surrounding the SNP positions. The
32,852 SNPs for which unambiguous positions could be found on genome assembly
version 4 were genotyped from the mapped WGS reads using \texttt{bcftools
mpileup} and \texttt{bcftools call}. We then used \texttt{bcftools gtcheck} to
compute the concordance between the WGS genotype calls and the
SoySNP50K genotype dataset. We identified 24 samples
with < 90\% concordance between the two genotype datasets and removed them from
the dataset. We also excluded an additional sample for which concordance was over 90\%
but poor raw sequencing data quality (\%GC content) suggested contamination.
The concordance between WGS data and SoySNP50K genotypes is included in
Additional file 3 and shown in Figure \ref{concordance-histogram}.

@@

None of the three GWAS analyses that we conducted on hilum color found signals
at the \emph{W1} and \emph{O} loci studied by \cite{bandillo2017} (Figures
\ref{hilum_color_blackbrown_manhattan} \ref{hilum_color_all_manhattan},
\ref{hilum_color_rbr_manhattan}).

### 2023-03-28 additional_files/main_text.tex
Fix some typos upon proofreading the manuscript

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{Td} locus for pubescence color. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{Td} locus. (b) Zoomed-in Manhattan plots at the \textit{Td} locus.
	The vertical dotted lines indicate the location of the
	Glyma.03g258700 gene associated with this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote points that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.03g258700. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrow indicates the
	direction of transcription. The red rectangle highlights the region
	shown in panel (d). (d) Pairwise alignment of the two haplotype
	sequences in the population at the \textit{Td} locus. Nucleotides are
	colored according to the
	\textit{p}-value of the most significant \textit{k}-mer overlapping
	them. The vertical dotted line between haplotypes indicates the location of
	the causal SNP at this locus. (e) Contingency table of
	the phenotypes and haplotypes found in the population at the
	\textit{Td} locus.}
\end{figure}

@@

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{G} locus for seed coat color. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{G} locus. (b) Zoomed-in Manhattan plots at the \textit{G} locus.
	The vertical dotted lines indicate the location of the
	Glyma.01g198500 gene associated with this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote points that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.01g198500. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrows indicate the
	direction of transcription. The red rectangle highlights the region
	shown in panel (d). (d) Pairwise alignment of the two haplotype
	sequences in the population at the \textit{G} locus. Nucleotides are
	colored according to the
	\textit{p}-value of the most significant \textit{k}-mer overlapping
	them. The vertical dotted line between haplotypes indicates the location of
	the causal SNP at this locus. (e) Contingency table of
	the phenotypes and haplotypes found in the population at the
	\textit{G} locus.}
\end{figure}

@@

% Pubescence density - Ps locus
\subsubsection*{Pubescence density -- Ps locus}
\label{sv-gwas-main-results-pubescence-density-ps}

@@

The difference in size between the CNV reported by \cite{liu2020ps} and our
results may be due to the presence of some unresolved sequence (a stretch of
4,635 'N' nucleotides) over that interval in the reference sequence that we used.
Because our SV filtering process removed any SV overlapping 'N' nucleotides in
the reference, we reasoned that the CNV may have been found by our pipeline but
filtered out later on. Indeed, we found a 42.8-kb duplication corresponding
to the one described above among the genotype calls made by smoove. An association
analysis of that single variant using GAPIT found a \textit{p}-value of 1.9e-23,
which would have made it the most significant SV. In this particular case, the
failure of the SV-based GWAS analysis to find identify the causal variant was due
to our filtering parameters and not to limitations of the SV genotype calls per se.

@@

% Seed coat luster - B locus
\subsubsection*{Seed coat luster -- B locus}
\label{sv-gwas-main-results-seed-coat-luster-b}

@@

The signals found by SNP- and \emph{k}-mer-based analyses at the \textit{L2}
locus overlap 24 and 50 genes, respectively (Additional file 1: Figures
\ref{pod_color_all_manhattan} and \ref{pod_color_all_L2_signal}). Despite this
somewhat high number, we noticed that the closest gene to the most significant
\emph{k}-mer (Glyma.03g005800) is also a MATE transporter, similarly to our top
candidate for \emph{L1}. This gene may therefore represent an interesting
candidate for this locus for future studies.

@@

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{Pa1} locus for pubescence form. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{Pa1} and \textit{Pa2} loci. (b) Zoomed-in Manhattan plots at the \textit{Pa1} locus.
	The vertical dotted lines indicate the location of the
	Glyma.12g213900 gene suggested as a candidate for this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote points that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.12g213900. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrows indicate the
	direction of transcription.
	(d) Manhattan plots at the location of the Glyma.12g213900 gene.
	Vertical lines indicate the location of two non-synonymous
	SNPs associated with appressed pubescence, which may represent causal variants
	at this locus. Panels (c) and (d) share the same x-axis.}
\end{figure}

@@

In addition to verifying known loci, we also observed potentially novel loci in
the \textit{k}-mer GWAS analysis of stem termination and pod color.  When
comparing accessions with indeterminate and semi-determinate stem termination
types, we observed previously undocumented signals on chromosomes Gm11, Gm16
and Gm18 in addition to the known \textit{Dt1} locus (Figure
\ref{stem-termination-main-figure}a).  Analysis of the pairwise LD between
significant \textit{k}-mers found no LD between these signals, suggesting that
they may represent \textit{bona fide} loci associated with stem termination
type (Figure \ref{stem-termination-main-figure}b). Similarly, a \textit{k}-mer
GWAS analysis comparing accessions with black and brown pods found a previously
undocumented signal on chromosome Gm15. \textit{k}-mers at this new locus
showed no LD with \textit{k}-mers at the known \textit{L1} locus and may
therefore represent a distinct locus (Additional file 1: Figures \ref{pod_color_blbr_manhattan} and
\ref{pod_color_blbr_ld}). The observed signal overlaps a total of 27 genes
(Additional file 1: Figure \ref{pod_color_blbr_pdcGm15_signal}), but none of those are annotated
as having an obvious role in controlling pod color.

@@

We used the reads retrieved by katcher and an assembly-based approach for
identifying the variants associated with a given set of \emph{k}-mers. In
addition to the reads themselves, we also retrieved their paired reads even
though they may not have matched a significant \emph{k}-mer in the first place.
These read pairs were used for \emph{de novo} assembly with SPAdes v. 3.15.4
\citep{spades} using the \texttt{--careful} parameter. The assemblies were done
individually for each accession and then aligned to the Williams82 reference
assembly using bwa mem with default parameters.  Aligned assembled sequences
that overlapped loci of interest were realigned using multiple sequence
alignment with the MAFFT program v. 7.475 \citep{katoh2002} for identifying and
visualizing the haplotypes at these loci. The identification of variants
supported by significant \textit{k}-mers was based entirely on visual analysis
of haplotype alignments. We only considered haplotypes occurring at least five
times in the population in such analyses in order to leave out potential
assembly errors. In a single case (\emph{Dt1} locus), assembly at the locus
succeeded for a very low number of accessions (26). In this case, we instead used
consensus sequences from the reads aligned with bwa for comparing the
haplotypes across accessions.

>>>>

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{Td} locus for pubescence color. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{Td} locus. (b) Zoomed-in Manhattan plots at the \textit{Td} locus.
	The vertical dotted lines indicate the location of the
	Glyma.03g258700 gene associated with this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote markers that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.03g258700. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrow indicates the
	direction of transcription. The red rectangle highlights the region
	shown in panel (d). (d) Pairwise alignment of the two haplotype
	sequences in the population at the \textit{Td} locus. Nucleotides are
	colored according to the
	\textit{p}-value of the most significant \textit{k}-mer overlapping
	them. The vertical dotted line between haplotypes indicates the location of
	the causal SNP at this locus. (e) Contingency table of
	the phenotypes and haplotypes found in the population at the
	\textit{Td} locus.}
\end{figure}

@@

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{G} locus for seed coat color. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{G} locus. (b) Zoomed-in Manhattan plots at the \textit{G} locus.
	The vertical dotted lines indicate the location of the
	Glyma.01g198500 gene associated with this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote markers that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.01g198500. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrows indicate the
	direction of transcription. The red rectangle highlights the region
	shown in panel (d). (d) Pairwise alignment of the two haplotype
	sequences in the population at the \textit{G} locus. Nucleotides are
	colored according to the
	\textit{p}-value of the most significant \textit{k}-mer overlapping
	them. The vertical dotted line between haplotypes indicates the location of
	the causal SNP at this locus. (e) Contingency table of
	the phenotypes and haplotypes found in the population at the
	\textit{G} locus.}
\end{figure}

@@

% Pubescence density - Ps locus
\subsubsection*{Pubescence density -- \textit{Ps} locus}
\label{sv-gwas-main-results-pubescence-density-ps}

@@

The difference in size between the CNV reported by \cite{liu2020ps} and our
results may be due to the presence of some unresolved sequence (a stretch of
4,635 N nucleotides) over that interval in the reference sequence that we used.
Because our SV filtering process removed any alternate allele containing N nucleotides,
we reasoned that the CNV may have been found by our pipeline but
filtered out later on. Indeed, we found a 42.8-kb duplication corresponding
to the one described above among the genotype calls made by smoove. An association
analysis of that single variant using GAPIT found a \textit{p}-value of 1.9e-23,
which would have made it the most significant SV. In this particular case, the
failure of the SV-based GWAS analysis to find identify the causal variant was due
to our filtering parameters and not to limitations of the SV genotype calls per se.

@@

% Seed coat luster - B locus
\subsubsection*{Seed coat luster -- \textit{B} locus}
\label{sv-gwas-main-results-seed-coat-luster-b}

@@

The signals found by SNP- and \emph{k}-mer-based analyses at the \textit{L2}
locus overlap 24 and 50 genes, respectively (Additional file 1: Figures
\ref{pod_color_all_manhattan} and \ref{pod_color_all_L2_signal}). Despite this
somewhat high number, we noticed that the closest gene to the most significant
\emph{k}-mer (Glyma.03g005800) is also a MATE transporter, similarly to our top
candidate for \emph{L1}. This gene may therefore represent an interesting
candidate at this locus for future studies.

@@

\begin{figure}
	\contcaption{Results of SNP- and \textit{k}-mer-based GWAS at the
	\textit{Pa1} locus for pubescence form. (a) Genome-wide Manhattan plots.
	Horizontal dotted lines indicate the significance
	threshold whereas vertical dotted lines indicate the location of the
	\textit{Pa1} and \textit{Pa2} loci. (b) Zoomed-in Manhattan plots at the \textit{Pa1} locus.
	The vertical dotted lines indicate the location of the
	Glyma.12g213900 gene suggested as a candidate for this locus. The shaded gray
	rectangles show the regions delimited by the top 1\% associations.
	In the case of SNPs, blue points denote markers used in the
	original analysis, whereas red points denote markers that had originally
	been pruned but whose \emph{p}-values were computed after signal
	discovery.
	(c) Gene model of Glyma.12g213900. Rectangles represent exons, colored
	rectangles represent coding sequences, and the arrows indicate the
	direction of transcription.
	(d) Manhattan plots at the location of the Glyma.12g213900 gene.
	Vertical lines indicate the location of two non-synonymous
	SNPs associated with appressed pubescence, which may represent causal variants
	at this locus. Panels (c) and (d) share the same x-axis.}
\end{figure}

@@

In addition to verifying known loci, we also observed potentially novel loci in
the \textit{k}-mer GWAS analysis of stem termination and pod color.  When
comparing accessions with indeterminate and semi-determinate stem termination
types, we observed previously undocumented signals on chromosomes Gm11, Gm16
and Gm18 in addition to the known \textit{Dt1} locus (Figure
\ref{stem-termination-main-figure}a).  Analysis of the pairwise LD between
significant \textit{k}-mers found no LD between these signals, suggesting that
they may represent \textit{bona fide} loci associated with stem termination
type (Figure \ref{stem-termination-main-figure}b). Similarly, a \textit{k}-mer
GWAS analysis comparing accessions with black and brown pods found a previously
undocumented signal on chromosome Gm15 (Additional file 1: Figure \ref{pod_color_blbr_manhattan}).
\textit{k}-mers at this new locus
showed no LD with \textit{k}-mers at the known \textit{L1} locus and may
therefore represent a distinct locus (Additional file 1: Figure 
\ref{pod_color_blbr_ld}). The observed signal overlaps a total of 27 genes
(Additional file 1: Figure \ref{pod_color_blbr_pdcGm15_signal}), but none of those are annotated
as having an obvious role in controlling pod color.

@@

We used the reads retrieved by katcher and an assembly-based approach for
identifying the variants associated with a given set of \emph{k}-mers. In
addition to the reads themselves, we also retrieved their paired reads even
though they may not have matched a significant \emph{k}-mer in the first place.
These read pairs were used for \emph{de novo} assembly with SPAdes v. 3.15.4
\citep{spades} using the \texttt{--careful} parameter. The assemblies were done
individually for each accession and then aligned to the Williams82 reference
assembly using bwa-mem with default parameters.  Aligned assembled sequences
that overlapped loci of interest were realigned using multiple sequence
alignment with the MAFFT program v. 7.475 \citep{katoh2002} for identifying and
visualizing the haplotypes at these loci. The identification of variants
supported by significant \textit{k}-mers was based entirely on visual analysis
of haplotype alignments. We only considered haplotypes occurring at least five
times in the population in such analyses in order to leave out potential
assembly errors. In a single case (\emph{Dt1} locus), assembly at the locus
succeeded for a very low number of accessions (26). In this case, we instead used
consensus sequences from the reads aligned with bwa for comparing the
haplotypes across accessions.

### 2023-03-28 additional_files/manuscript.tex
Fix some typos upon proofreading the manuscript

% Defining a new command for signal plot figures
\newcommand{\signalplot}[4]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_signal}
	\caption[Zoomed-in Manhattan plots of the #3 locus]{Zoomed-in Manhattan plots of signals detected by the GWAS analysis of #2 at the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	Panel (a) shows gene models over the genomic interval.
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	#4
	Gray shaded rectangles indicate the region delimited by the top 5\% (SVs) or top 1\% (SNPs/indels and \emph{k}-mers) associations in the signal region.
	In the case of SNPs/indels, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	}
	\label{#1_signal}
\end{cfigure}

@@

% Defining a new command for gene plot figures
\newcommand{\geneplot}[5]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_gene}
	\caption[Zoomed-in Manhattan plots of the #3 locus gene]%
	{Zoomed-in Manhattan plots generated from the GWAS analysis of #2 at the #4 associated with the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	#5
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	In the case of SNPs/indels, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	Panel (a) shows gene models over the plotting interval.
	Exons are represented by rectangles whereas introns are represented by horizontal lines.
	Coding sequences are shown in blue and the direction of transcription is indicated by arrows.
	}
	\label{#1_gene}
\end{cfigure}

>>>>

% Defining a new command for signal plot figures
\newcommand{\signalplot}[4]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_signal}
	\caption[Zoomed-in Manhattan plots of the #3 locus]{Zoomed-in Manhattan plots of signals detected by the GWAS analysis of #2 at the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	Panel (a) shows gene models over the genomic interval.
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	#4
	Gray shaded rectangles indicate the region delimited by the top 5\% (SVs) or top 1\% (SNPs/indels and \emph{k}-mers) associations in the signal region.
	In the case of SNPs/indels, blue points denote markers used in the original analysis, whereas red points denote markers that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	}
	\label{#1_signal}
\end{cfigure}

@@

% Defining a new command for gene plot figures
\newcommand{\geneplot}[5]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_gene}
	\caption[Zoomed-in Manhattan plots of the #3 locus gene]%
	{Zoomed-in Manhattan plots generated from the GWAS analysis of #2 at the #4 associated with the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	#5
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	In the case of SNPs/indels, blue points denote markers used in the original analysis, whereas red points denote markers that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	Panel (a) shows gene models over the plotting interval.
	Exons are represented by rectangles whereas introns are represented by horizontal lines.
	Coding sequences are shown in blue and the direction of transcription is indicated by arrows.
	}
	\label{#1_gene}
\end{cfigure}
